### 2013-12-11 paper/paper.tex
NOW WIT PICTURES

% \epigraphsize{\small}% Default
\setlength\epigraphwidth{16cm}
\setlength\epigraphrule{1pt}

@@

% insert the table of contents
\tableofcontents
\listoffigures
\listoftables
\epigraph{THIS SHOULD REALLY BE A QUOTE}{ \textup{ZACH}}

@@

\subsection{Machine Learning Algorithms}
\subsection{Pull Requests}
\section{Results}
\subsection{Data}
\subsection{Analysis}
\subsection{Threats to Validity}
\section{Concluding Remarks}

>>>>

% \epigraphsize{\small}% Default
\setlength\epigraphwidth{16cm}
\setlength\epigraphrule{1pt}
\usepackage[margin=1.25in]{geometry}

@@

% insert the table of contents
\tableofcontents
\listoffigures
\listoftables
\epigraph{Yeah Science!!}{ \textup{Jesse Pinkman}}

@@

\subsection{Machine Learning Algorithms}
\subsection{Pull Requests}
\section{Results}
\subsection{Data}
\subsection{Feature Analysis}
We went through several iterations of features to represent commits; we will briefly touch here on the features that did not work well before continuing to a more lengthy discussion of the features we actually used.  Our first attempt at classifying commits attempted to cast this prediction problem as equivalent to catching email spam.  A simple way to predict that an email is to train on the individual words in spam email.  The more a word is associated with being seen only in spam email, the more likely an email containing that word is spam.  We attempted to apply this to commits by training a Naive Bayes learner on the words of a commit messages. This turned out to be a not-very-good idea, with results about as good as randomly guessing clean or buggy.  Abandoning the buggy commit as email spam metaphor, we decided to look at attributes of the commit.

   The features we chose to represent our commits are fairly simple ones; of the commit attribute data we use, only the day of the week required any computation.  Most of these attributes are presented to the user by git when they make a commit.  We did some initial testing with a decision tree learner, inspecting changes in results while testing differnt subsets of features.  We also manually kept track of which features were pruned from the tree, which indicates they are less informative.   We concluded Time and Date commit data is not very informative for the open source projects we chose to study.  Year and Month are too large to contain much signal, day of month and minute are too specific.  Because hour is not stored in local time and the generally distributed nature of these projects, we did not find Hour to be an informative feature.  It is possible that these features could be more valuable in a highly centralized development structure, where there is extra knowledge of development schedules and other information, but without any additional knowledge, we decided to ignore specific time-date data.

\subsection{Testing Methodology}

To test the effectiveness of our feature selection, we mined features from eight open source repositories.  We attempted to choose projects with different life spans and applications to make our results more generalizable.  The list of projects mined, their number of commits, and the percentage of those commits we found to be buggy are in table {CITE}.

\begin{table}[h]
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |}
    \hline
    Repository & Start Date & $\#$  Commits & $\#$ Buggy  Commits & \% Buggy \\ \hline
    one     & June 2008   &   8179 & 2744 & 33.6 \\ \hline
    cyclus & March 2010 &  2162 & 1071 & 49.5 \\ \hline
    git        & April 2005    &   28788 & 10682 & 37.1 \\ \hline
    jedit &Sept 1998 &  6890 & 3190 & 46.3 \\ \hline
    jquery     & March 2006   &   5608 & 3074 & 54.8 \\ \hline
    puppet & April 2005 &  12174 & 4812 & 39.5 \\ \hline
    scala     & Feb 2003   &   20398 & 9584 & 47.0 \\ \hline
    scipy & Feb 2001 &  10035 & 3252 & 32.4 \\ \hline        	
    \end{tabular}
\end{center}\caption{Mined Repositories}
\label{tab:repos}
\end{table}

  For each repository we mined, we took the year of 2013, regardless of its size, to be our test set.  The reasoning behind this is that in practice, users will want to classify new commits as they come in, and the most recent year of commits were the best fit of the data we had. Notice due to the way our heuristic works (start at a bug fix and work back) our test set is likely to contain more false negatives because the bug fixes have potentially not been written yet.  However, in practice this will also be the case so we feel this should not unreasonably skew our results.
 \begin{figure}[h]
\centering
	\includegraphics[width=0.75\textwidth]{images/history}
\caption{Testing and Training Sets}
\label{git_comp}

\end{figure}

 	For training data, we took commits from the final day of 2012 back six months, one year, two year, and to the start of the repository.  The goal here is to see how our results change with more data to train on (and potentially overfit to).

	\begin{table}[h]
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |c|}
    \hline

Repo & Test Set & 6Mo Train  & 1 Yr Train   & 2 Yr Train & All Train \\ \hline

one &  2304  &  1190 &  2423 & 4367  &  5874 \\ \hline
cyclus & 546  & 389  & 1231  & 1524  & 1616 \\ \hline
git & 2916  & 1369  & 2630  & 5129  & 25869 \\ \hline
jedit & 165  & 301  & 760  & 1401  & 6725 \\ \hline
jquery & 898  & 592  & 925  & 1934  & 4695 \\ \hline
puppet & 2195  & 980  & 2130  & 3854  & 9979 \\ \hline
scala & 1752  & 1347  & 2983  & 5080  & 18644 \\ \hline
scipy & 1873  & 546  & 1130  & 1786  & 8162 \\ \hline

\end{tabular}
\end{center}\caption{Size of Training and Test Sets}
\label{tab:size}
\end{table}

	\begin{table}[h]
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |c|}
    \hline

Repo & Test Set & 6Mo Train  & 1 Yr Train   & 2 Yr Train & All Train \\ \hline

one  & 23.1 & 26.4 & 30.2 & 35.4 & 37.7 \\ \hline 
cyclus  & 30.6 & 44.4 & 50.6 & 54.9 & 55.9 \\ \hline 
git  & 13.9 & 22.1 & 22.5 & 23.4 & 39.7 \\ \hline
jedit  & 6.7 & 13.9 & 24.7 & 23.1 & 47.3 \\ \hline
jquery  & 35.7 & 43.2 & 46.6 & 53.9 & 58.6 \\ \hline 
puppet  & 18.7 & 20.0 & 26.1 & 29.1 & 44.1 \\ \hline 
scala  & 27.2 & 45.3 & 48.8 & 50.3 & 48.9 \\ \hline 
scipy  & 18.8 & 23.6 & 23.6 & 24.7 & 35.5 \\ \hline
\end{tabular}
\end{center}\caption{Bugginess of Training and Test Sets}
\label{tab:buggy}
\end{table}

\subsection{Learner Accuracy}

 \begin{figure}[h]
\centering
	\includegraphics[width=0.75\textwidth]{images/learner_comp}
\caption{Comparison of Feature Results - 6 Months}
\label{git_comp}

\end{figure}

\subsection{Training Set Variation}

 \begin{figure}[h]
\centering
	\includegraphics[width=0.75\textwidth]{images/time_comp}
\caption{Training Data Size - Message and Attributes}
\label{git_comp}

\end{figure}

\subsection{Cross Repository Training}

Six months to a year of repository data before being able to use a tool seems like a fairly high price of admission.  Being able to substitute another repository’s history for your own with little to no hit in accuracy seems like it would make our tool more applicable.  Furthermore, what does this say about commits if commits from two unrelated repositories are similar enough that one can be used to train the other?  To answer these questions, we decided to use git’s commit history to train our learner and test on the other seven repositories.  Git was chosen because it was the repository with the best nontrivial performance.  In order for training and testing data to be compatible, the user feature had to be removed from both data sets.

 \begin{figure}[h]
\centering
	\includegraphics[width=0.6\textwidth]{images/git_comp}
\caption{Training With Git - 6 Months, Message and Attribute Data}
\label{git_comp}

\end{figure}

In general, results tended to be comparable to those using their respective data sets.  The git learner accuracies displayed the same trend of slow decrease as training data size increased, with a noticeable drop when all training data was used.  As Table [CITE] shows, cyclus and jquery see drop offs of about four percentage points, while scala performs six percentage points better.  The other four repositories stay essentially the same, with some minor variation.  Interestingly, the git trained learner is able to slightly improve on the always-guess-clean jedit learner even though the git training data is three times as buggy as the jedit test data.

This comparable performance indicates to us that using a learner trained on another repository is a valid proxy for repositories that do not have their own history.  It also seems that the distribution of message and commit attribute features we use do not vary much across repositories.  More work would need to be done to give such a claim actual weight, but if our features have global, general boundaries, could we use this information in some kind of prescriptive fashion, a la “keep your commits to X lines added if possible”. Or would knowledge and enforcement of this information simply shift the boundary?

\subsection{Threats to Validity}

There are several potential threats to the validity of our results.  The heuristic used in classifying past commits represents a multifaceted threat.  First, though [CITE] has presented some evidence that this method works well in practice, there is no evidence to support that these results generalize well.  As we mined neither of the two projects they studied, it is possible that our approximation of the true distribution of clean and buggy commits is flawed.  Even if we had mined those repositories, it is possible in the eight years between the writing of [CITE] and now that the heuristic does as well.  Another potential problem this heuristic introduces is that our ensemble learner is attempting to learn this approximation.  If the approximation does not closely match the actual distribution, then the results we present are in no way an indication of how our tool would perform against actual commits.

Another potential threat is the repositories we chose.  While we attempted to pick a representative sample of the open source projects in development, this excludes closed source projects. Also, we only mined english-speaking repositories, which is required by our heuristic classification and all of our message features.  We made no attempt to take into account differences and eccentricities of the individual repositories we did mine.  It is possible (even likely) that these eccentricities are to account for the variation between repositories.

\section{Concluding Remarks}
